\section{Related Work}
\label{sec:related}

\textbf{Surgical outcome simulation.} Preoperative visualization predates
generative models by decades: manual computer morphing measurably improves
rhinoplasty patient satisfaction~\cite{sharp2002computerimaging}, its
expectation-management risks are equally well documented~\cite{agarwal2007morph},
and 3D simulation accuracy correlates with postoperative
satisfaction~\cite{yamamichi2025crisalix,threedvr2026aesthetic}. Learning-based
successors train bespoke models per procedure: a GAN trained on 3{,}030 paired
rhinoplasty photographs whose outputs raters could not distinguish from real
post-ops~\cite{knoedler2024rhinoplastygan}, appearance predictors for
blepharoptosis~\cite{blepharoptosis2022poap,huang2024ptosisdiffusion}, and
biomechanics-driven craniofacial simulation~\cite{fang2022acmtnet}; a recent
systematic review surveys the area~\cite{stephanian2024fpsamreview}. Closest to us,
Envisage~\cite{agarwal2026envisage} combines a local FLUX-based inpainter with
MediaPipe masks, hard compositing, and a mask-decomposed score for rhinoplasty. We
differ on each axis that defines our question: we benchmark six hosted black-box
APIs rather than one open-weight model, on two procedures rather than one, with
control itself as the manipulated variable. Lim et
al.~\cite{lim2023generativecosmetic} prompt text-to-image tools about the same
procedures but generate generic faces rather than editing a patient's photo.

\textbf{Training-free localized editing.} Methods that confine an edit without
fine-tuning uniformly reach inside the model: SDEdit, RePaint, and DiffEdit steer
the sampling loop~\cite{meng2022sdedit,lugmayr2022repaint,couairon2023diffedit},
Blended (Latent) Diffusion blends masked latents at every denoising
step~\cite{avrahami2022blended,avrahami2023blendedlatent}, and Prompt-to-Prompt
and Plug-and-Play inject attention or
features~\cite{hertz2023prompt2prompt,tumanyan2023plugandplay}. A hosted endpoint
exposes none of those surfaces. Our masked composite is deliberately the
post-hoc remnant of this family---the final pixel-space blend, applied after the
API returns---and the paper measures how far that remnant carries.

\textbf{Benchmarking instruction-guided editors.} General-domain benchmarks are
plentiful~\cite{brooks2023instructpix2pix,zhang2023magicbrush,wang2023editbench,
sheynin2024emuedit,ku2024imagenhub,ma2024i2ebench,hui2025hqedit,liu2025step1xedit},
and hosted commercial editors are now benchmarked
routinely~\cite{gptimgeval2025,qian2025giebench}. Off-target measurement also has
precedent: GIE-Bench scores object-masked preservation and finds GPT-Image
over-edits irrelevant regions~\cite{qian2025giebench}, and ALE-Bench quantifies
attribute leakage outside the edit target~\cite{alebench2024}. None of these
address faces in a clinical setting, pair region confinement with identity as dual
failure modes, or validate against real post-operative photographs---the three
elements our protocol combines. ArcFace cosine itself is the standard identity
measure in face editing~\cite{deng2019arcface}; we claim the pairing and the
per-rung reading, not the metric.

\textbf{Face analysis.} The pipeline builds on MediaPipe's face
mesh~\cite{lugaresi2019mediapipe,grishchenko2020attentionmesh} with InsightFace's
SCRFD detection and landmarks as the profile fallback~\cite{guo2022scrfd}, and on
CIELAB color difference~\cite{sharma2005ciede2000} for the regional metric.
