\section{Experimental Setup}
\label{sec:setup}

\begin{table}[t]
  \centering
  \caption{Models in the study. Hosted models run behind fal.ai endpoints; cost is
  the provider's per-image estimate at the pinned date.}
  \label{tab:models}
  \resizebox{\columnwidth}{!}{\input{tables/setup_models}}
\end{table}

\textbf{Models.} Table~\ref{tab:models} lists the lineup: six hosted
editors---OpenAI GPT Image~2 at two quality tiers~\cite{openai2026gptimage2},
Google's Nano Banana~Pro and Nano
Banana~2~\cite{google2025nanobananapro,google2025nanobanana}, ByteDance
Seedream~5.0~\cite{seedream5_2026,seedream4_2025}, and
FLUX.2~[pro]~\cite{bfl2025fluxkontext}---plus Qwen-Image-Edit as a hosted
inpainting endpoint for the masked-inpaint rung~\cite{wu2025qwenimage}. The same
model is available as open weights for a privacy-sensitive local deployment
track, which we do not benchmark here. Hosted models are moving targets, so every
run records its date and the exact endpoint identifier.

\textbf{Data.} The full pool contains real, licensed before/after photograph
pairs: 12 frontal deep-plane-facelift inputs (11 with a paired post-operative
photograph) and 14 rhinoplasty inputs (10 profile views and 4 frontal
cross-views, all paired). The benchmark matrix uses 8 facelift faces and 8
rhinoplasty faces (the 4 frontal cross-views, which the regional metric can
score, plus 4 profiles that contribute identity and ground-truth evidence).
Images are normalized to $1024^2$ with padding. The datasets are licensed for AI
use and republication; no private patient data was used at any point. Synthetic
candidate faces were piloted early in the project and abandoned for quality
reasons, so all results below are on real faces.

\textbf{Protocol.} Runs expand a Cartesian matrix of faces $\times$ models
$\times$ procedures $\times$ controls with a fixed seed, so every cell exists and
none can be quietly dropped: the gallery renderer shows the full grid, and model
failures are recorded in the results table rather than raised. Each run directory
is immutable and stores the resolved configuration and the git commit that produced
it; output filenames encode the full cell key, which is also the join key for
scoring. Generation and scoring are decoupled, so metrics can be recomputed without
touching images. The reported results come from a registered set of matrix runs
executed together, after the pipeline was frozen; earlier development runs are
retained but not pooled into the statistics. A final experiment chains two
procedures on the same face in both orders (rhinoplasty then facelift, and the
reverse) to test whether region-confined stages compose. Across all scored edits
the median latency is \MedLatency{}\,s and the median cost \$\MedCost{} per
image.

The paper itself is generated from this provenance: every number in the text and
tables is produced by an aggregation script from the run records, with duplicate
cells resolved by keeping the most completely scored row.
